Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola

### 2023-01-19 Manuscript/manuscript_files/supplemental.tex
Updated tables in supplemental

\begin{longtable}{l|l|r|r|r|r|r|l|r|r}
\caption{Summary of parameters for commodity canola models} \\

@@

Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\

@@

\multicolumn{10}{@{}l}{\textit{(continued)}}\\

@@

 & Intercept & 3.76 & 0.05 & 3.77 & 3.66 & 3.87 & $<$0.0001 & 855 & 1.005\\
\cline{2-10}
 & HB distance & 0.02 & 0.01 & 0.02 & 0.00 & 0.04 & 0.0868 & 10154 & 1.000\\
\cline{2-10}
 & Sigma & 0.31 & 0.02 & 0.31 & 0.28 & 0.34 & - & 5039 & 0.999\\
\cline{2-10}
\multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.37 & 0.04 & 0.37 & 0.30 & 0.46 & - & 3774 & 1.000\\
\cline{1-10}
 & Intercept & 5.24 & 0.24 & 5.24 & 4.77 & 5.72 & $<$0.0001 & 2108 & 1.001\\
\cline{2-10}
 & Plant density & -0.70 & 0.06 & -0.70 & -0.82 & -0.57 & $<$0.0001 & 2097 & 1.001\\
\cline{2-10}
 & HB distance & 0.03 & 0.01 & 0.03 & 0.01 & 0.06 & 0.0095 & 9212 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.22 & 0.04 & 0.22 & 0.15 & 0.29 & - & 1456 & 1.000\\
\cline{2-10}
\multirow{-5}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.64 & 0.02 & 0.64 & 0.61 & 0.68 & - & 7845 & 0.999\\
\cline{1-10}
 & Intercept & 5.74 & 4.70 & 5.70 & -3.62 & 15.01 & 0.222 & 1822 & 1.001\\
\cline{2-10}
 & Plant size & -1.66 & 0.98 & -1.66 & -3.60 & 0.25 & 0.0926 & 1632 & 1.001\\
\cline{2-10}
 & HB distance & 0.75 & 0.11 & 0.75 & 0.53 & 0.96 & $<$0.0001 & 6878 & 1.000\\
\cline{2-10}
 & Plant density & -0.41 & 0.74 & -0.42 & -1.86 & 1.06 & 0.5792 & 2243 & 1.001\\
\cline{2-10}
 & Sigma & 3.52 & 0.17 & 3.51 & 3.19 & 3.87 & - & 4976 & 0.999\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.55 & 0.39 & 3.53 & 2.88 & 4.40 & - & 4133 & 1.000\\
\cline{1-10}
 & Intercept & -1.98 & 0.45 & -1.96 & -2.89 & -1.17 & $<$0.0001 & 936 & 1.006\\
\cline{2-10}
 & HB distance & -0.31 & 0.10 & -0.31 & -0.50 & -0.13 & 0.0011 & 3526 & 1.001\\
\cline{2-10}
 & Number of hives & 0.72 & 0.15 & 0.72 & 0.43 & 1.04 & $<$0.0001 & 1534 & 1.003\\
\cline{2-10}
 & Flower density & 0.03 & 0.04 & 0.03 & -0.06 & 0.12 & 0.541 & 2397 & 1.000\\
\cline{2-10}
 & Sigma (field) & 1.44 & 0.34 & 1.43 & 0.80 & 2.14 & - & 494 & 1.014\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.35 & 0.08 & 0.34 & 0.22 & 0.53 & - & 1630 & 1.003\\
\cline{1-10}
 & Intercept & 2.56 & 0.04 & 2.56 & 2.50 & 2.63 & $<$0.0001 & 594 & 1.006\\
\cline{2-10}
 & Plant size & 0.94 & 0.01 & 0.94 & 0.92 & 0.96 & $<$0.0001 & 1709 & 1.002\\
\cline{2-10}
 & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
\cline{2-10}
 & Phi (field) & 0.16 & 0.02 & 0.16 & 0.13 & 0.19 & - & 3461 & 1.000\\
\cline{2-10}
 & Intercept (Phi) & 2.17 & 0.32 & 2.17 & 1.56 & 2.81 & - & 1517 & 1.001\\
\cline{2-10}
 & Plant size (Phi) & 0.66 & 0.11 & 0.66 & 0.44 & 0.87 & - & 1587 & 1.002\\
\cline{2-10}
\multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.66 & 0.12 & 0.65 & 0.45 & 0.90 & - & 844 & 1.005\\
\cline{1-10}
 & Intercept & 0.66 & 0.08 & 0.66 & 0.50 & 0.82 & $<$0.0001 & 1946 & 0.999\\
\cline{2-10}
 & HB visits & 0.00 & 0.03 & 0.00 & -0.05 & 0.05 & 0.96 & 3292 & 1.000\\
\cline{2-10}
 & Plant size & 0.13 & 0.03 & 0.13 & 0.08 & 0.18 & $<$0.0001 & 3345 & 1.000\\
\cline{2-10}
 & Pollen count & 0.16 & 0.11 & 0.15 & -0.05 & 0.38 & 0.1515 & 638 & 1.002\\
\cline{2-10}
 & Sigma (field) & 0.29 & 0.03 & 0.29 & 0.23 & 0.37 & - & 2675 & 1.000\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
\cline{1-10}
 & Intercept & 25.07 & 1.77 & 25.07 & 21.64 & 28.54 & $<$0.0001 & 2277 & 1.000\\
\cline{2-10}
 & HB visits & 0.17 & 0.21 & 0.17 & -0.24 & 0.60 & 0.4284 & 4417 & 1.000\\
\cline{2-10}
 & Pollen count & -0.97 & 0.84 & -0.98 & -2.60 & 0.68 & 0.2447 & 707 & 1.003\\
\cline{2-10}
 & Plant size & 4.31 & 0.65 & 4.31 & 3.03 & 5.58 & $<$0.0001 & 2229 & 1.000\\
\cline{2-10}
 & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
\cline{2-10}
 & Flowers per plant & -2.80 & 0.65 & -2.79 & -4.08 & -1.55 & $<$0.0001 & 2105 & 1.000\\
\cline{2-10}
 & Sigma & 4.06 & 0.12 & 4.06 & 3.83 & 4.29 & - & 6604 & 1.000\\
\cline{2-10}
 & Sigma (field) & 1.98 & 0.26 & 1.96 & 1.51 & 2.53 & - & 2526 & 0.999\\
\cline{2-10}
\multirow{-9}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.00 & 1.03 & 1.74 & 0.84 & 4.64 & - & 3265 & 1.000\\
\cline{1-10}
 & Intercept & 0.64 & 0.54 & 0.64 & -0.40 & 1.72 & 0.2367 & 1402 & 1.000\\
\cline{2-10}
 & HB visits & 0.02 & 0.04 & 0.02 & -0.05 & 0.09 & 0.6113 & 2748 & 1.000\\
\cline{2-10}
 & Pollen count & -0.15 & 0.17 & -0.15 & -0.48 & 0.20 & 0.3744 & 358 & 1.008\\
\cline{2-10}
 & Seeds per pod & 0.00 & 0.01 & 0.00 & -0.01 & 0.02 & 0.4508 & 3348 & 1.000\\
\cline{2-10}
 & Plant size & -0.03 & 0.12 & -0.03 & -0.26 & 0.20 & 0.7955 & 1633 & 1.000\\
\cline{2-10}
 & Plant density & 0.30 & 0.08 & 0.30 & 0.14 & 0.45 & 0.0001 & 1704 & 1.001\\
\cline{2-10}
 & HB distance & 0.02 & 0.01 & 0.02 & -0.01 & 0.05 & 0.1686 & 1404 & 1.003\\
\cline{2-10}
 & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
\cline{2-10}
 & Flowers per plant & 0.11 & 0.12 & 0.11 & -0.13 & 0.34 & 0.363 & 1526 & 1.000\\
\cline{2-10}
 & Flower density & -0.03 & 0.01 & -0.03 & -0.04 & -0.02 & $<$0.0001 & 2213 & 1.003\\
\cline{2-10}
 & Sigma & 0.52 & 0.03 & 0.52 & 0.46 & 0.59 & - & 2100 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.47 & 0.05 & 0.47 & 0.37 & 0.58 & - & 2828 & 0.999\\
\cline{2-10}
\multirow{-13}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.71 & 0.48 & 2.63 & 2.08 & 3.86 & - & 1792 & 1.001\\

@@

>>>>

% \begin{longtable}{l|l|r|r|r|r|r|l|r|r} %First manuscript
% \caption{Summary of parameters for commodity canola models} \\
% \hline
% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
% \hline
% \endfirsthead
% \multicolumn{10}{@{}l}{\textit{(continued)}}\\
% \hline
% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
% \hline
% \endhead
%  & Intercept & 3.76 & 0.05 & 3.77 & 3.66 & 3.87 & $<$0.0001 & 855 & 1.005\\
% \cline{2-10}
%  & HB distance & 0.02 & 0.01 & 0.02 & 0.00 & 0.04 & 0.0868 & 10154 & 1.000\\
% \cline{2-10}
%  & Sigma & 0.31 & 0.02 & 0.31 & 0.28 & 0.34 & - & 5039 & 0.999\\
% \cline{2-10}
% \multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.37 & 0.04 & 0.37 & 0.30 & 0.46 & - & 3774 & 1.000\\
% \cline{1-10}
%  & Intercept & 5.24 & 0.24 & 5.24 & 4.77 & 5.72 & $<$0.0001 & 2108 & 1.001\\
% \cline{2-10}
%  & Plant density & -0.70 & 0.06 & -0.70 & -0.82 & -0.57 & $<$0.0001 & 2097 & 1.001\\
% \cline{2-10}
%  & HB distance & 0.03 & 0.01 & 0.03 & 0.01 & 0.06 & 0.0095 & 9212 & 1.000\\
% \cline{2-10}
%  & Sigma (field) & 0.22 & 0.04 & 0.22 & 0.15 & 0.29 & - & 1456 & 1.000\\
% \cline{2-10}
% \multirow{-5}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.64 & 0.02 & 0.64 & 0.61 & 0.68 & - & 7845 & 0.999\\
% \cline{1-10}
%  & Intercept & 5.74 & 4.70 & 5.70 & -3.62 & 15.01 & 0.222 & 1822 & 1.001\\
% \cline{2-10}
%  & Plant size & -1.66 & 0.98 & -1.66 & -3.60 & 0.25 & 0.0926 & 1632 & 1.001\\
% \cline{2-10}
%  & HB distance & 0.75 & 0.11 & 0.75 & 0.53 & 0.96 & $<$0.0001 & 6878 & 1.000\\
% \cline{2-10}
%  & Plant density & -0.41 & 0.74 & -0.42 & -1.86 & 1.06 & 0.5792 & 2243 & 1.001\\
% \cline{2-10}
%  & Sigma & 3.52 & 0.17 & 3.51 & 3.19 & 3.87 & - & 4976 & 0.999\\
% \cline{2-10}
% \multirow{-6}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.55 & 0.39 & 3.53 & 2.88 & 4.40 & - & 4133 & 1.000\\
% \cline{1-10}
%  & Intercept & -1.98 & 0.45 & -1.96 & -2.89 & -1.17 & $<$0.0001 & 936 & 1.006\\
% \cline{2-10}
%  & HB distance & -0.31 & 0.10 & -0.31 & -0.50 & -0.13 & 0.0011 & 3526 & 1.001\\
% \cline{2-10}
%  & Number of hives & 0.72 & 0.15 & 0.72 & 0.43 & 1.04 & $<$0.0001 & 1534 & 1.003\\
% \cline{2-10}
%  & Flower density & 0.03 & 0.04 & 0.03 & -0.06 & 0.12 & 0.541 & 2397 & 1.000\\
% \cline{2-10}
%  & Sigma (field) & 1.44 & 0.34 & 1.43 & 0.80 & 2.14 & - & 494 & 1.014\\
% \cline{2-10}
% \multirow{-6}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.35 & 0.08 & 0.34 & 0.22 & 0.53 & - & 1630 & 1.003\\
% \cline{1-10}
%  & Intercept & 2.56 & 0.04 & 2.56 & 2.50 & 2.63 & $<$0.0001 & 594 & 1.006\\
% \cline{2-10}
%  & Plant size & 0.94 & 0.01 & 0.94 & 0.92 & 0.96 & $<$0.0001 & 1709 & 1.002\\
% \cline{2-10}
%  & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
% \cline{2-10}
%  & Phi (field) & 0.16 & 0.02 & 0.16 & 0.13 & 0.19 & - & 3461 & 1.000\\
% \cline{2-10}
%  & Intercept (Phi) & 2.17 & 0.32 & 2.17 & 1.56 & 2.81 & - & 1517 & 1.001\\
% \cline{2-10}
%  & Plant size (Phi) & 0.66 & 0.11 & 0.66 & 0.44 & 0.87 & - & 1587 & 1.002\\
% \cline{2-10}
% \multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.66 & 0.12 & 0.65 & 0.45 & 0.90 & - & 844 & 1.005\\
% \cline{1-10}
%  & Intercept & 0.66 & 0.08 & 0.66 & 0.50 & 0.82 & $<$0.0001 & 1946 & 0.999\\
% \cline{2-10}
%  & HB visits & 0.00 & 0.03 & 0.00 & -0.05 & 0.05 & 0.96 & 3292 & 1.000\\
% \cline{2-10}
%  & Plant size & 0.13 & 0.03 & 0.13 & 0.08 & 0.18 & $<$0.0001 & 3345 & 1.000\\
% \cline{2-10}
%  & Pollen count & 0.16 & 0.11 & 0.15 & -0.05 & 0.38 & 0.1515 & 638 & 1.002\\
% \cline{2-10}
%  & Sigma (field) & 0.29 & 0.03 & 0.29 & 0.23 & 0.37 & - & 2675 & 1.000\\
% \cline{2-10}
% \multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
% \cline{1-10}
%  & Intercept & 25.07 & 1.77 & 25.07 & 21.64 & 28.54 & $<$0.0001 & 2277 & 1.000\\
% \cline{2-10}
%  & HB visits & 0.17 & 0.21 & 0.17 & -0.24 & 0.60 & 0.4284 & 4417 & 1.000\\
% \cline{2-10}
%  & Pollen count & -0.97 & 0.84 & -0.98 & -2.60 & 0.68 & 0.2447 & 707 & 1.003\\
% \cline{2-10}
%  & Plant size & 4.31 & 0.65 & 4.31 & 3.03 & 5.58 & $<$0.0001 & 2229 & 1.000\\
% \cline{2-10}
%  & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
% \cline{2-10}
%  & Flowers per plant & -2.80 & 0.65 & -2.79 & -4.08 & -1.55 & $<$0.0001 & 2105 & 1.000\\
% \cline{2-10}
%  & Sigma & 4.06 & 0.12 & 4.06 & 3.83 & 4.29 & - & 6604 & 1.000\\
% \cline{2-10}
%  & Sigma (field) & 1.98 & 0.26 & 1.96 & 1.51 & 2.53 & - & 2526 & 0.999\\
% \cline{2-10}
% \multirow{-9}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.00 & 1.03 & 1.74 & 0.84 & 4.64 & - & 3265 & 1.000\\
% \cline{1-10}
%  & Intercept & 0.64 & 0.54 & 0.64 & -0.40 & 1.72 & 0.2367 & 1402 & 1.000\\
% \cline{2-10}
%  & HB visits & 0.02 & 0.04 & 0.02 & -0.05 & 0.09 & 0.6113 & 2748 & 1.000\\
% \cline{2-10}
%  & Pollen count & -0.15 & 0.17 & -0.15 & -0.48 & 0.20 & 0.3744 & 358 & 1.008\\
% \cline{2-10}
%  & Seeds per pod & 0.00 & 0.01 & 0.00 & -0.01 & 0.02 & 0.4508 & 3348 & 1.000\\
% \cline{2-10}
%  & Plant size & -0.03 & 0.12 & -0.03 & -0.26 & 0.20 & 0.7955 & 1633 & 1.000\\
% \cline{2-10}
%  & Plant density & 0.30 & 0.08 & 0.30 & 0.14 & 0.45 & 0.0001 & 1704 & 1.001\\
% \cline{2-10}
%  & HB distance & 0.02 & 0.01 & 0.02 & -0.01 & 0.05 & 0.1686 & 1404 & 1.003\\
% \cline{2-10}
%  & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
% \cline{2-10}
%  & Flowers per plant & 0.11 & 0.12 & 0.11 & -0.13 & 0.34 & 0.363 & 1526 & 1.000\\
% \cline{2-10}
%  & Flower density & -0.03 & 0.01 & -0.03 & -0.04 & -0.02 & $<$0.0001 & 2213 & 1.003\\
% \cline{2-10}
%  & Sigma & 0.52 & 0.03 & 0.52 & 0.46 & 0.59 & - & 2100 & 1.000\\
% \cline{2-10}
%  & Sigma (field) & 0.47 & 0.05 & 0.47 & 0.37 & 0.58 & - & 2828 & 0.999\\
% \cline{2-10}
% \multirow{-13}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.71 & 0.48 & 2.63 & 2.08 & 3.86 & - & 1792 & 1.001\\
% \hline
% \end{longtable}
% \endgroup{}
\begin{longtable}{l|l|r|r|l|l|l}
\caption{Summary of parameters for commodity canola models. p-values indicate whether means differed from zero (variance terms were excluded). Means are also shown for 2014 and 2015 models, with * indicating whether parameters differed between years (i.e. posterior 95\% quantiles did not overlap).} \\

@@

Model & Parameter & Mean & SD & p-value & Mean$_{2014}$ & Mean$_{2015}$\\

@@

\multicolumn{7}{@{}l}{\textit{(continued)}}\\

@@

 & HB distance & 0.016 & 0.010 & 0.0868 & 0.02 & 0.012\\
\cline{2-7}
 & Sigma & 0.309 & 0.016 & - & 0.307 & 0.318\\
\cline{2-7}
\multirow{-3}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.371 & 0.040 & - & 0.387 & 0.365\\
\cline{1-7}
 & Plant density & -0.695 & 0.063 & $<$0.0001 & -0.826 & -0.492\\
\cline{2-7}
 & HB distance & 0.032 & 0.012 & 0.0095 & 0.025 & 0.042\\
\cline{2-7}
 & Sigma (field) & 0.217 & 0.036 & - & 0.189 & 0.196\\
\cline{2-7}
\multirow{-4}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.640 & 0.018 & - & 0.65 & 0.626\\
\cline{1-7}
 & Plant size & -1.658 & 0.985 & 0.0926 & -0.602 & -2.193\\
\cline{2-7}
 & HB distance & 0.750 & 0.111 & $<$0.0001 & 0.885 & 0.518\\
\cline{2-7}
 & Plant density & -0.409 & 0.737 & 0.5792 & -0.573 & 0.279\\
\cline{2-7}
 & Sigma & 3.520 & 0.171 & - & 3.965* & 2.663*\\
\cline{2-7}
\multirow{-5}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.554 & 0.389 & - & 3.779 & 2.834\\
\cline{1-7}
 & HB distance & -0.313 & 0.096 & 0.0011 & -0.442 & -0.262\\
\cline{2-7}
 & Number of hives & 0.720 & 0.153 & $<$0.0001 & 0.848 & 0.654\\
\cline{2-7}
 & Flower density & 0.028 & 0.045 & 0.541 & 0.137 & -0.117\\
\cline{2-7}
 & Sigma (field) & 1.441 & 0.340 & - & 1.019 & 1.383\\
\cline{2-7}
\multirow{-5}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.350 & 0.080 & - & 0.29 & 0.396\\
\cline{1-7}
 & Plant size & 0.937 & 0.010 & $<$0.0001 & 0.935 & 0.946\\
\cline{2-7}
 & Pods per plant & -0.162 & 0.013 & $<$0.0001 & -0.136* & -0.242*\\
\cline{2-7}
 & Phi (field) & 0.160 & 0.016 & - & 0.141 & 0.165\\
\cline{2-7}
 & Plant size (Phi) & 0.659 & 0.110 & - & 0.884* & 0.196*\\
\cline{2-7}
\multirow{-5}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.660 & 0.116 & - & 0.61 & 0.897\\
\cline{1-7}
 & HB visits & 0.001 & 0.026 & 0.96 & 0.003 & 0.033\\
\cline{2-7}
 & Plant size & 0.133 & 0.026 & $<$0.0001 & 0.108 & 0.167\\
\cline{2-7}
 & Pollen count & 0.158 & 0.110 & 0.1515 & 0.244 & 0.045\\
\cline{2-7}
 & Sigma (field) & 0.294 & 0.034 & - & 0.351 & 0.231\\
\cline{2-7}
\multirow{-5}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.346 & 0.067 & - & 3.036* & 3.975*\\
\cline{1-7}
 & HB visits & 0.170 & 0.214 & 0.4284 & 0.262 & 0.342\\
\cline{2-7}
 & Pollen count & -0.974 & 0.837 & 0.2447 & 0.219 & -2.117\\
\cline{2-7}
 & Plant size & 4.310 & 0.650 & $<$0.0001 & 3.855 & 2.899\\
\cline{2-7}
 & Pods per plant & 0.557 & 0.288 & 0.0529 & 0.722 & 0.623\\
\cline{2-7}
 & Flowers per plant & -2.799 & 0.648 & $<$0.0001 & -2.221 & -1.576\\
\cline{2-7}
 & Sigma & 4.057 & 0.117 & - & 4.243 & 3.744\\
\cline{2-7}
 & Sigma (field) & 1.976 & 0.261 & - & 1.591 & 1.517\\
\cline{2-7}
\multirow{-8}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.001 & 1.029 & - & 1.714 & 1.855\\
\cline{1-7}
 & HB visits & 0.019 & 0.037 & 0.6113 & -0.033 & 0.027\\
\cline{2-7}
 & Pollen count & -0.152 & 0.171 & 0.3744 & -0.341 & 0.147\\
\cline{2-7}
 & Seeds per pod & 0.004 & 0.006 & 0.4508 & -0.001 & 0.014\\
\cline{2-7}
 & Plant size & -0.031 & 0.118 & 0.7955 & 0.143 & -0.332\\
\cline{2-7}
 & Plant density & 0.298 & 0.078 & 0.0001 & 0.289 & 0.353\\
\cline{2-7}
 & HB distance & 0.021 & 0.015 & 0.1686 & -0.013 & 0.076\\
\cline{2-7}
 & Pods per plant & 0.108 & 0.045 & 0.0159 & 0.126 & 0.042\\
\cline{2-7}
 & Flowers per plant & 0.110 & 0.121 & 0.363 & -0.033 & 0.357\\
\cline{2-7}
 & Flower density & -0.030 & 0.007 & $<$0.0001 & -0.022 & -0.04\\
\cline{2-7}
 & Sigma & 0.520 & 0.033 & - & 0.492 & 0.542\\
\cline{2-7}
 & Sigma (field) & 0.468 & 0.052 & - & 0.416 & 0.494\\
\cline{2-7}
\multirow{-12}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.714 & 0.478 & - & 2.478 & 3.234\\

@@

% \begingroup\fontsize{9}{11}\selectfont %First manuscript
% \begin{longtable}{l|l|r|r|r|r|r|l|r|r}
% \caption{Summary of parameters for seed canola models} \\
% \hline
% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
% \hline
% \endfirsthead
% \multicolumn{10}{@{}l}{\textit{(continued)}}\\
% \hline
% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
% \hline
% \endhead
%  & Intercept & 3.60 & 0.06 & 3.60 & 3.47 & 3.73 & $<$0.0001 & 524 & 1.004\\
% \cline{2-10}
%  & HB distance & 0.06 & 0.01 & 0.06 & 0.04 & 0.07 & $<$0.0001 & 5750 & 0.999\\
% \cline{2-10}
%  & Sigma & 0.27 & 0.01 & 0.27 & 0.24 & 0.30 & - & 5199 & 0.999\\
% \cline{2-10}
% \multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.36 & 0.05 & 0.36 & 0.28 & 0.48 & - & 4182 & 1.000\\
% \cline{1-10}
%  & Intercept & 6.08 & 0.25 & 6.08 & 5.57 & 6.56 & $<$0.0001 & 2480 & 1.000\\
% \cline{2-10}
%  & Plant density & -0.79 & 0.07 & -0.80 & -0.92 & -0.66 & $<$0.0001 & 2470 & 1.000\\
% \cline{2-10}
%  & HB distance & 0.07 & 0.01 & 0.07 & 0.05 & 0.10 & $<$0.0001 & 6446 & 0.999\\
% \cline{2-10}
%  & Sigma & 0.50 & 0.03 & 0.50 & 0.45 & 0.56 & - & 2332 & 1.000\\
% \cline{2-10}
%  & Sigma (field) & 0.15 & 0.04 & 0.15 & 0.08 & 0.23 & - & 1053 & 1.001\\
% \cline{2-10}
% \multirow{-6}{*}{\raggedright\arraybackslash Plant size} & Nu (DF) & 1.91 & 0.32 & 1.87 & 1.37 & 2.65 & $<$0.0001 & 2700 & 1.000\\
% \cline{1-10}
%  & Intercept & 0.48 & 0.56 & 0.46 & -0.58 & 1.64 & 0.3827 & 661 & 1.005\\
% \cline{2-10}
%  & HB distance & 1.11 & 0.12 & 1.11 & 0.87 & 1.36 & $<$0.0001 & 5389 & 1.000\\
% \cline{2-10}
%  & Sigma & 4.06 & 0.24 & 4.05 & 3.59 & 4.56 & - & 2404 & 1.001\\
% \cline{2-10}
%  & Sigma (field) & 3.48 & 0.47 & 3.44 & 2.70 & 4.49 & - & 2640 & 1.001\\
% \cline{2-10}
% \multirow{-5}{*}{\raggedright\arraybackslash Flower density} & Nu (DF) & 1.88 & 0.38 & 1.84 & 1.30 & 2.68 & $<$0.0001 & 1500 & 1.004\\
% \cline{1-10}
%  & Intercept & 3.08 & 0.10 & 3.08 & 2.87 & 3.28 & $<$0.0001 & 2722 & 1.002\\
% \cline{2-10}
%  & Flower density & -0.01 & 0.01 & -0.01 & -0.03 & 0.01 & 0.5267 & 4150 & 1.000\\
% \cline{2-10}
%  & HB distance & -0.02 & 0.05 & -0.03 & -0.12 & 0.07 & 0.6229 & 4410 & 1.000\\
% \cline{2-10}
%  & LCB distance & 0.42 & 0.09 & 0.42 & 0.24 & 0.58 & $<$0.0001 & 5053 & 1.000\\
% \cline{2-10}
%  & Bay centre & 0.45 & 0.21 & 0.45 & 0.07 & 0.88 & 0.0284 & 6486 & 0.999\\
% \cline{2-10}
%  & Phi & 0.72 & 0.09 & 0.72 & 0.55 & 0.92 & - & 4354 & 1.001\\
% \cline{2-10}
%  & Theta (ZI) & 0.32 & 0.03 & 0.32 & 0.26 & 0.38 & - & 3955 & 1.001\\
% \cline{2-10}
% \multirow{-8}{*}{\raggedright\arraybackslash HB visits} & Sigma (field) & 0.41 & 0.11 & 0.41 & 0.22 & 0.64 & - & 600 & 1.001\\
% \cline{1-10}
%  & Intercept & 2.25 & 0.14 & 2.25 & 1.96 & 2.51 & $<$0.0001 & 1734 & 1.002\\
% \cline{2-10}
%  & LCB distance & -0.79 & 0.07 & -0.79 & -0.94 & -0.65 & $<$0.0001 & 4016 & 1.000\\
% \cline{2-10}
%  & HB distance & -0.32 & 0.06 & -0.32 & -0.43 & -0.21 & $<$0.0001 & 5128 & 1.000\\
% \cline{2-10}
%  & Bay centre & -0.34 & 0.23 & -0.34 & -0.77 & 0.16 & 0.1458 & 6667 & 1.000\\
% \cline{2-10}
%  & Flower density & 0.03 & 0.01 & 0.03 & 0.01 & 0.05 & 0.0115 & 4364 & 1.000\\
% \cline{2-10}
%  & Sigma (field) & 0.63 & 0.13 & 0.62 & 0.40 & 0.91 & - & 1072 & 1.004\\
% \cline{2-10}
%  & Phi & 0.70 & 0.11 & 0.69 & 0.50 & 0.93 & - & 3097 & 0.999\\
% \cline{2-10}
% \multirow{-8}{*}{\raggedright\arraybackslash LCB visits} & Theta (ZI) & 0.25 & 0.04 & 0.25 & 0.15 & 0.33 & - & 2383 & 1.000\\
% \cline{1-10}
%  & Intercept & 2.49 & 0.19 & 2.50 & 2.12 & 2.85 & $<$0.0001 & 1141 & 1.002\\
% \cline{2-10}
%  & HB visits & 0.05 & 0.04 & 0.05 & -0.03 & 0.12 & 0.195 & 2317 & 1.000\\
% \cline{2-10}
%  & LCB visits & 0.15 & 0.06 & 0.14 & 0.02 & 0.26 & 0.0155 & 2239 & 1.000\\
% \cline{2-10}
%  & Bay centre & -0.55 & 0.13 & -0.55 & -0.80 & -0.30 & $<$0.0001 & 2540 & 1.000\\
% \cline{2-10}
%  & HB distance & -0.17 & 0.04 & -0.17 & -0.25 & -0.09 & $<$0.0001 & 2265 & 1.003\\
% \cline{2-10}
%  & LCB distance & -0.35 & 0.14 & -0.35 & -0.63 & -0.07 & 0.0164 & 2513 & 1.000\\
% \cline{2-10}
%  & Flower density & -0.03 & 0.02 & -0.03 & -0.06 & 0.01 & 0.1284 & 2058 & 1.001\\
% \cline{2-10}
%  & Sigma (field) & 0.86 & 0.13 & 0.85 & 0.64 & 1.15 & - & 2978 & 1.000\\
% \cline{2-10}
%  & Sigma (plot) & 0.65 & 0.06 & 0.65 & 0.53 & 0.78 & - & 1142 & 1.003\\
% \cline{2-10}
% \multirow{-10}{*}{\raggedright\arraybackslash Pollen count} & Phi & 0.82 & 0.04 & 0.82 & 0.74 & 0.90 & - & 5125 & 0.999\\
% \cline{1-10}
%  & Intercept & 3.05 & 0.04 & 3.05 & 2.96 & 3.14 & $<$0.0001 & 3283 & 0.999\\
% \cline{2-10}
%  & Plant size & 0.93 & 0.01 & 0.93 & 0.90 & 0.95 & $<$0.0001 & 3712 & 0.999\\
% \cline{2-10}
%  & Bay centre & 0.09 & 0.02 & 0.09 & 0.06 & 0.12 & $<$0.0001 & 6790 & 0.999\\
% \cline{2-10}
%  & Pods per plant & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\
% \cline{2-10}
%  & Sigma (field) & 0.08 & 0.01 & 0.08 & 0.06 & 0.11 & - & 2649 & 1.000\\
% \cline{2-10}
%  & Intercept (Phi) & 2.24 & 0.32 & 2.24 & 1.62 & 2.87 & - & 2875 & 1.001\\
% \cline{2-10}
% \multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & Plant size (Phi) & 0.38 & 0.10 & 0.39 & 0.19 & 0.57 & - & 2871 & 1.001\\
% \cline{1-10}
%  & Intercept & 0.18 & 0.12 & 0.18 & -0.05 & 0.40 & 0.1211 & 2261 & 1.000\\
% \cline{2-10}
%  & Pollen count & 0.12 & 0.04 & 0.12 & 0.03 & 0.20 & 0.0074 & 915 & 1.004\\
% \cline{2-10}
%  & Plant size & 0.19 & 0.03 & 0.19 & 0.14 & 0.24 & $<$0.0001 & 4570 & 1.000\\
% \cline{2-10}
%  & Bay centre & -0.21 & 0.06 & -0.21 & -0.33 & -0.10 & 0.0003 & 1886 & 1.000\\
% \cline{2-10}
%  & HB distance & -0.12 & 0.02 & -0.12 & -0.15 & -0.08 & $<$0.0001 & 1929 & 1.002\\
% \cline{2-10}
%  & LCB distance & -0.21 & 0.06 & -0.21 & -0.34 & -0.10 & 0.0005 & 2637 & 1.000\\
% \cline{2-10}
%  & Flower density & 0.00 & 0.01 & 0.00 & -0.02 & 0.01 & 0.5456 & 2998 & 1.000\\
% \cline{2-10}
%  & Sigma (plot) & 0.30 & 0.03 & 0.30 & 0.25 & 0.35 & - & 1367 & 1.004\\
% \cline{2-10}
